\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-09-28 paper/manuscript.tex
addressed point on sample selection

For data availability reasons, on which we elaborate below, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas. These states provide us with a sample that is well-balanced on a number of theoretically important indicators. One, each of the four geographic regions are represented with at least one state. Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities and less densely populated areas are covered. Furthermore, the sample is politically balanced---we have three blue states (CA, WA, NY) and three red states (TX, IN, LA). Finally, our dataset contains some of the wealthiest states (NY, CA, WA and TX are \#2, \#8, \#9 and \#16 respectively, by GDP per capita \citep{BureauofEconomicAnalysis2017}), but also some of the poorer ones (IN and LA).

>>>>

For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas. The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data. Municipal elections in Indiana and Louisiana are partisan across the board,\footnote{In Indiana, this includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.} so our sample is primarily focused on these two states. Here, all cities with a website are included, resulting in a considerably larger sample than for the other four states. New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see below for more detail on how we use this data). Finally, California and Texas contain a number of large cities, whose mayors are sufficiently well-known for their partisanship to be available. These six states also provide us with a sample that is well-balanced on a number of theoretically important indicators. One, each of the four geographic regions are represented with at least one state. Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities and less densely populated areas are covered. Furthermore, the sample is politically balanced---we have three blue states (CA, WA, NY) and three red states (TX, IN, LA). Finally, our dataset contains some of the wealthiest states (NY, CA, WA and TX are \#2, \#8, \#9 and \#16 respectively, by GDP per capita \citep{BureauofEconomicAnalysis2017}), but also some of the poorer ones (IN and LA).
